Toronto's Most Studious Wards:  An Analysis of Annual Toronto Public Library's Circulation and Visits by Wards Prior to and Post-COVID

### 2024-01-25 outputs/paper/paper.qmd
paper update

---
title: "Toronto's Most Studious Wards:  An Analysis of Annual Toronto Public Library's Circulation and Visits by Wards Prior to and Post-COVID"
subtitle: "Data Visualization in R"
author:
  - Francesca Ye
email: francesca.ye@mail.utoronto.ca
prerequisites: "Datasets taken from opensourcetoronto and can be found here: https://open.toronto.ca/catalogue/"
date: January 22 2024 
date-format: long
abstract: "Toronto Public Library data sets on branch information, annual circulation, and annual visits were used to examine library usage patterns by ward between 2018 and 2022. Based on the analysis of annual circulation and visits by ward over this five year period, there is evidence that library usage significantly dropped in 2020 when comparing values to 2018 and 2019. Looking beyond the initial outbreak of COVID-19, it also appears that library usage is beginning to recover, although not to pre-pandemic levels, which highlight differences in pre and post-pandemic library usage. It would be beneficial to expand the scope of the analysis to more years before and after 2020 to get a larger sample of library usage patterns in addition to analysis of monthly circulation and visitiation data against a timeline of government mandated COVID-19 measures."
format: pdf
toc: true
number-sections: true
bibliography: references.bib
---
```{r}
#| warning: false
#| message: false
#| echo: false

@@

```{r}
#| warning: false
#| message: false
#| echo: false
#| label: fig-circulation2018
#| fig-cap: Total 2018 Annual Circulation of Toronto Public Library Branches (Physical and Fixed Location Branches Only) by Ward
#| fig-pos: "H"

@@

```{r}
#| warning: false
#| message: false
#| echo: false
#| label: fig-circulation2019
#| fig-cap: Total 2019 Annual Circulation of Toronto Public Library Branches (Physical and Fixed Location Branches Only) by Ward
#| fig-pos: "H"

@@

```{r}
#| warning: false
#| message: false
#| echo: false
#| label: fig-circulation2020
#| fig-cap: Total 2020 Annual Circulation of Toronto Public Library Branches (Physical and Fixed Location Branches Only) by Ward
#| fig-pos: "H"

@@

```{r}
#| warning: false
#| message: false
#| echo: false
#| label: fig-circulation2021
#| fig-cap: Total 2021 Annual Circulation of Toronto Public Library Branches (Physical and Fixed Location Branches Only) by Ward
#| fig-pos: "H"

@@

```{r}
#| warning: false
#| message: false
#| echo: false
#| label: fig-circulation2022
#| fig-cap: Total 2022 Annual Circulation of Toronto Public Library Branches (Physical and Fixed Location Branches Only) by Ward
#| fig-pos: "H"

@@

```{r}
#| warning: false
#| message: false
#| echo: false
#| label: fig-visits2018
#| fig-cap: Total 2018 Annual Visits of Toronto Public Library Branches (Physical and Fixed Location Branches Only) by Ward
#| fig-pos: "H"

@@

```{r}
#| warning: false
#| message: false
#| echo: false
#| label: fig-visits2019
#| fig-cap: Total 2019 Annual Visits of Toronto Public Library Branches (Physical and Fixed Location Branches Only) by Ward
#| fig-pos: "H"

@@

```{r}
#| warning: false
#| message: false
#| echo: false
#| label: fig-visits2020
#| fig-cap: Total 2020 Annual Visits of Toronto Public Library Branches (Physical and Fixed Location Branches Only) by Ward
#| fig-pos: "H"

@@

```{r}
#| warning: false
#| message: false
#| echo: false
#| label: fig-visits2021
#| fig-cap: Total 2021 Annual Visits of Toronto Public Library Branches (Physical and Fixed Location Branches Only) by Ward
#| fig-pos: "H"

@@

```{r}
#| warning: false
#| message: false
#| echo: false
#| label: fig-visits2022
#| fig-cap: Total 2022 Annual Visits of Toronto Public Library Branches (Physical and Fixed Location Branches Only) by Ward
#| fig-pos: "H"

>>>>

---
title: "Toronto's Most Studious Wards:  An Analysis of Annual Toronto Public Library's Circulation and Visits by Wards Prior to and Post-COVID"
subtitle: "Data Visualization in R"
author:
  - Francesca Ye
email: francesca.ye@mail.utoronto.ca
prerequisites: "Datasets taken from opensourcetoronto and can be found here: https://open.toronto.ca/catalogue/"
date: today 
date-format: long
abstract: "Toronto Public Library data sets on branch information, annual circulation, and annual visits were used to examine library usage patterns by ward between 2018 and 2022. Based on the analysis of annual circulation and visits by ward over this five year period, there is evidence that library usage significantly dropped in 2020 when comparing values to 2018 and 2019. Looking beyond the initial outbreak of COVID-19, it also appears that library usage is beginning to recover, although not to pre-pandemic levels, which highlight differences in pre and post-pandemic library usage. It would be beneficial to expand the scope of the analysis to more years before and after 2020 to get a larger sample of library usage patterns in addition to analysis of monthly circulation and visitiation data against a timeline of government mandated COVID-19 measures."
format: pdf
toc: true
number-sections: true
bibliography: references.bib
---
```{r}
#| warning: false
#| message: false
#| echo: false

@@

```{r}
#| warning: false
#| message: false
#| echo: false
#| label: fig-circulation2018
#| fig-cap: Total 2018 Annual Circulation of Toronto Public Library Branches (Physical and Fixed Location Branches Only) by Ward
#| fig-pos: "H"
#| fig-height: 2.2

@@

```{r}
#| warning: false
#| message: false
#| echo: false
#| label: fig-circulation2019
#| fig-cap: Total 2019 Annual Circulation of Toronto Public Library Branches (Physical and Fixed Location Branches Only) by Ward
#| fig-pos: "H"
#| fig-height: 2.2

@@

```{r}
#| warning: false
#| message: false
#| echo: false
#| label: fig-circulation2020
#| fig-cap: Total 2020 Annual Circulation of Toronto Public Library Branches (Physical and Fixed Location Branches Only) by Ward
#| fig-pos: "H"
#| fig-height: 2.2

@@

```{r}
#| warning: false
#| message: false
#| echo: false
#| label: fig-circulation2021
#| fig-cap: Total 2021 Annual Circulation of Toronto Public Library Branches (Physical and Fixed Location Branches Only) by Ward
#| fig-pos: "H"
#| fig-height: 2.2

@@

```{r}
#| warning: false
#| message: false
#| echo: false
#| label: fig-circulation2022
#| fig-cap: Total 2022 Annual Circulation of Toronto Public Library Branches (Physical and Fixed Location Branches Only) by Ward
#| fig-pos: "H"
#| fig-height: 2.2

@@

```{r}
#| warning: false
#| message: false
#| echo: false
#| label: fig-visits2018
#| fig-cap: Total 2018 Annual Visits of Toronto Public Library Branches (Physical and Fixed Location Branches Only) by Ward
#| fig-pos: "H"
#| fig-height: 2.2

@@

```{r}
#| warning: false
#| message: false
#| echo: false
#| label: fig-visits2019
#| fig-cap: Total 2019 Annual Visits of Toronto Public Library Branches (Physical and Fixed Location Branches Only) by Ward
#| fig-pos: "H"
#| fig-height: 2.2

@@

```{r}
#| warning: false
#| message: false
#| echo: false
#| label: fig-visits2020
#| fig-cap: Total 2020 Annual Visits of Toronto Public Library Branches (Physical and Fixed Location Branches Only) by Ward
#| fig-pos: "H"
#| fig-height: 2.2

@@

```{r}
#| warning: false
#| message: false
#| echo: false
#| label: fig-visits2021
#| fig-cap: Total 2021 Annual Visits of Toronto Public Library Branches (Physical and Fixed Location Branches Only) by Ward
#| fig-pos: "H"
#| fig-height: 2.2

@@

```{r}
#| warning: false
#| message: false
#| echo: false
#| label: fig-visits2022
#| fig-cap: Total 2022 Annual Visits of Toronto Public Library Branches (Physical and Fixed Location Branches Only) by Ward
#| fig-pos: "H"
#| fig-height: 2.2
